Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-06-27 code/rmarkdown/article.Rmd
+ fix bug in si figures

<!--  title page -->
Short running title: Genetic surrogates in conservation \newline
Word count: XXXXX \newline
Number of references: XXXX \newline
Number of figures: XXXX \newline
Number of tables: XXXX \newline
Number of text boxes: XXXX \newline
\newpage

>>>>

<!--  title page -->
Short running title: Genetic surrogates in conservation \newline
Abstract word count: XXXXX \newline
Main text word count: XXXXX \newline
Number of references: XXXX \newline
Number of equations: XXXX \newline
Number of figures: XXXX \newline
Number of tables: XXXX \newline
Number of text boxes: XXXX \newline
\newpage
